systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-12-03 paper/trunk/systemfit_compare_lm.tex
a minor improvement and a minor correction in the appendix comparing the objects returned by systemfit and lm
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@868 591db2bd-e0a0-4d22-8c19-2192dbb7da31

\code{systemfit} returns a list of class \code{systemfit}
that contains all results that belong to the entire system
of equations.
One special element of this list called \code{eq}.
It is a list that contains one object for each estimated equation.
These objects are of the class \code{systemfit.equation}
and contain the results that belong only to the regarding equation.

>>>>

\code{systemfit} returns a list of class \code{systemfit}
that contains the results that belong to the entire system
of equations.
One special element of this list is called \code{eq}.
It is a list that contains one object for each estimated equation.
These objects are of the class \code{systemfit.equation}
and contain the results that belong only to the regarding equation.
